Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-11-19 demystify.tex
updates

In recent years many universities start requiring a statement about diversity, equity, and inclusion (DEI) as part of the application (also see \autoref{sec:urm}). Students, especially international ones, often wonder what to write about, especially if they are not from a minority group, have not experienced anything related the topic, or even not sure what it is about.

>>>>

Many universities now require a diversity, equity, and inclusion (DEI) statement as part of the application (also see \autoref{sec:urm}). Students, especially international ones, often struggle with what to write, especially when they are not from a minority group or do not have much experience in DEI.
